signalHsmm - a novel semi-Markov model of eukaryotic signal peptides

### 2015-06-19 paper.tex
ready for dr Mackiewicz

\begin{table}[ht]
\centering
\caption{Comparison of Area Under the Curve, Sensitivity, Specificity and Matthews Correlation Coefficient for different classifiers.} 
\begin{tabular}{lrrrr}
  \toprule
Software name & AUC & Sensitivity & Specificity & MCC \\ 
  \midrule
signalP 4.1 (no tm) \citep{2011petersensignalp} & 0.9424 & 0.9720 & 0.9128 & 0.8859 \\ 
   \rowcolor[gray]{0.85}signalP 4.1 (tm) \citep{2011petersensignalp} & 0.9675 & 0.9579 & 0.9771 & 0.9353 \\ 
  PrediSi \citep{2004hillerpredisi} & 0.8959 & 0.9065 & 0.8853 & 0.7919 \\ 
   \rowcolor[gray]{0.85}Phobius \citep{2004klla} & 0.9515 & 0.9673 & 0.9358 & 0.9033 \\ 
  Philius \citep{2008reynoldstransmembrane} & 0.9376 & 0.9533 & 0.9220 & 0.8755 \\ 
   \rowcolor[gray]{0.85}signalHsmm-2010 & 0.9429 & 0.9393 & 0.8761 & 0.8166 \\ 
  signalHsmm-1989 & 0.9455 & 0.9486 & 0.8945 & 0.8440 \\ 
   \bottomrule
\end{tabular}
\label{tab:bench2010}
\end{table}

@@

\begin{table}[ht]
\centering
\caption{Comparison of Area Under the Curve, H-measure and Matthews Correlation Coefficient for different classifiers considering only proteins belonging to Plasmodiidae.} 
\begin{tabular}{lrrrr}
  \toprule
Software name & AUC & Sensitivity & Specificity & MCC \\ 
  \midrule
signalP 4.1 (no tm) \citep{2011petersensignalp} & 0.7928 & 0.6471 & 0.9385 & 0.6185 \\ 
   \rowcolor[gray]{0.85}PrediSi \citep{2004hillerpredisi} & 0.6597 & 0.3725 & 0.9469 & 0.4028 \\ 
  Phobius \citep{2004klla} & 0.7963 & 0.6765 & 0.9162 & 0.5991 \\ 
   \rowcolor[gray]{0.85}Philius \citep{2008reynoldstransmembrane} & 0.7753 & 0.6176 & 0.9330 & 0.5841 \\ 
  signalHsmm-2010 & 0.9340 & 0.7941 & 0.8939 & 0.6526 \\ 
   \rowcolor[gray]{0.85}signalHsmm-1989 & 0.9326 & 0.9216 & 0.8966 & 0.7531 \\ 
   \bottomrule
\end{tabular}
\label{tab:bench2010plas}
\end{table}

>>>>

\begin{table}[ht]
\centering
\caption{Comparison of Area Under the Curve, Sensitivity, Specificity and Matthews Correlation Coefficient for different classifiers.} 
\begin{tabular}{lrrrr}
  \toprule
Software name & AUC & Sensitivity & Specificity & MCC \\ 
  \midrule
signalP 4.1 (no tm) \citep{2011petersensignalp} & 0.9416 & 0.9720 & 0.9112 & 0.8848 \\ 
   \rowcolor[gray]{0.85}signalP 4.1 (tm) \citep{2011petersensignalp} & 0.9673 & 0.9579 & 0.9766 & 0.9347 \\ 
  PrediSi \citep{2004hillerpredisi} & 0.8949 & 0.9065 & 0.8832 & 0.7899 \\ 
   \rowcolor[gray]{0.85}Phobius \citep{2004klla} & 0.9509 & 0.9673 & 0.9346 & 0.9024 \\ 
  Philius \citep{2008reynoldstransmembrane} & 0.9369 & 0.9533 & 0.9206 & 0.8743 \\ 
   \rowcolor[gray]{0.85}signalHsmm-2010 & 0.9526 & 0.9533 & 0.8832 & 0.8385 \\ 
  signalHsmm-1989 & 0.9562 & 0.9626 & 0.8972 & 0.8617 \\ 
   \rowcolor[gray]{0.85}signalHsmm-2010 with k-mers & 0.9679 & 0.9673 & 0.9112 & 0.8799 \\ 
   \bottomrule
\end{tabular}
\label{tab:bench2010}
\end{table}

@@

\begin{table}[ht]
\centering
\caption{Comparison of Area Under the Curve, H-measure and Matthews Correlation Coefficient for different classifiers considering only proteins belonging to Plasmodiidae.} 
\begin{tabular}{lrrrr}
  \toprule
Software name & AUC & Sensitivity & Specificity & MCC \\ 
  \midrule
signalP 4.1 (no tm) \citep{2011petersensignalp} & 0.7928 & 0.6471 & 0.9385 & 0.6185 \\ 
   \rowcolor[gray]{0.85}PrediSi \citep{2004hillerpredisi} & 0.6597 & 0.3725 & 0.9469 & 0.4028 \\ 
  Phobius \citep{2004klla} & 0.7963 & 0.6765 & 0.9162 & 0.5991 \\ 
   \rowcolor[gray]{0.85}Philius \citep{2008reynoldstransmembrane} & 0.7753 & 0.6176 & 0.9330 & 0.5841 \\ 
  signalHsmm-2010 & 0.9340 & 0.7941 & 0.8939 & 0.6526 \\ 
   \rowcolor[gray]{0.85}signalHsmm-1989 & 0.9326 & 0.9216 & 0.8966 & 0.7531 \\ 
  signalHsmm-2010 with k-mers & 0.9334 & 0.9902 & 0.7989 & 0.6767 \\ 
   \bottomrule
\end{tabular}
\label{tab:bench2010plas}
\end{table}
